---
title: "Vast Mini Challenge 2 - Answer"
author: "Jovinka Hartanto"
date: "7/13/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.retina = 3)
```

```{r install packages and load library, include=FALSE}
packages = c('raster', 'sf', 'st',
             'tmap','mapview', 'clock', 
             'tidyverse','plotly','lubridate', 'ggiraph', 'plotly', 
             'DT', 'patchwork',
             'tidyverse','ggplot2','data.table','ggraph')
for (p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}

```

## Question 1
Using just the credit and loyalty card data, identify the most popular locations, and when they are popular. What anomalies do you see? What corrections would you recommend to correct these anomalies? Please limit your answer to 8 images and 300 words.

## Answer

### Popular Location

By observing loyalty and credit card data, we can observe that the top three most popular location during the 2 weeks data are Katerina's Cafe followed by Hippokampos, and Guy's Gyros.

As showed in the data table below, both loyalty and credit card data shows a consistent result for the popular location.


```{r import cc data and loyalty card data, include=FALSE}
loyalty_data <- read_csv("MC2/loyalty_data.csv")

loyalty_data$timestamp <- date_time_parse(loyalty_data$timestamp,
                                zone = "",
                                format = "%m/%d/%Y")
for(i in 1:nrow(loyalty_data))
{
  if(loyalty_data$location[i] %like% "Katerina") 
  {
  loyalty_data$location[i] <- str_replace(loyalty_data$location[i],loyalty_data$location[i],"Katerina's Cafe") 
  }
}

cc_data <- read_csv("MC2/cc_data.csv")

cc_data$timestamp_date <- date_time_parse(cc_data$timestamp,
                                zone = "",
                                format = "%m/%d/%Y")
cc_data$timestamp <- date_time_parse(cc_data$timestamp,
                                zone = "",
                                format = "%m/%d/%Y %H:%M")
cc_data$time = format(cc_data$timestamp, format = "%H:%M")
cc_data$hours = get_hour(cc_data$timestamp)
cc_data$day = weekdays(cc_data$timestamp)

for(i in 1:nrow(cc_data))
{
  if(cc_data$location[i] %like% "Katerina") 
  {
   cc_data$location[i] <- str_replace(cc_data$location[i],cc_data$location[i],"Katerina's Cafe") 
  }
}

```

```{r cc freq and cc loyalty, echo=FALSE}
cc_freq <- group_by(cc_data, location) %>% summarise(freq = n())%>% arrange(desc(freq))
datatable(cc_freq, 
          caption = 'Credit Card Frequency')

loyalty_freq <- group_by(loyalty_data, location) %>% summarise(freq = n())%>% arrange(desc(freq))
datatable(loyalty_freq,
          caption = 'Loyalty Card Frequency')

```
Stacked bar below shows which date are the most popular for the these popular place based on loyalty and credit card data, which apparently shows a different results.Based on loyalty card transaction data **Katerina's Cafe** was popular on **11 January 2014**, with 19 transactions from GASTech employees. **Hippokampos** has the most transaction on **8 January 2014** and lastly **Guy's Gyros** has the most transaction on **15 January 2014**.
However based on credit card data **Katerina's Cafe** is most popular on **6 January 2014**, **Hippokampos** on **16 January 2014** and **Guy's Gyros** on **13 January 2014**


``` {r loyalty and  cc top 3 daily frequency, echo = FALSE}
loyalty_freq_daily <- group_by(loyalty_data, timestamp, location) %>% summarise(freq = n())%>% arrange(desc(freq))
top3_place = c("Katerina's Cafe", "Hippokampos","Guy's Gyros")

loyalty_freq_daily_selected <- loyalty_freq_daily %>% filter(location %in% top3_place)

top3_vis_L <- ggplot(loyalty_freq_daily_selected, aes(fill=as.character(timestamp), y=freq, x=location)) + 
    geom_bar(position="stack", stat="identity") +
    geom_text(label = loyalty_freq_daily_selected$freq, position=position_stack(vjust=0.5))+
    ggtitle("Loyalty data top 3 location")

ggplotly(top3_vis_L)


cc_freq_daily <- group_by(cc_data, timestamp_date, location) %>% summarise(freq = n())%>% arrange(desc(freq))
top3_place = c("Katerina's Cafe", "Hippokampos","Guy's Gyros")

cc_freq_daily_selected <- cc_freq_daily %>% filter(location %in% top3_place)

top3_vis_cc <- ggplot(cc_freq_daily_selected, aes(fill=as.character(timestamp_date), y=freq, x=location)) + 
    geom_bar(position="stack", stat="identity") +
    geom_text(label = cc_freq_daily_selected$freq, position=position_stack(vjust=0.5))+
    ggtitle("CC data top 3 location")

ggplotly(top3_vis_cc)



```
Interactive bar graph was created below by using credit card dara to observe the patterns of visiting the top three locations in different hours of the day. We can see that most of the GASTech employee visited Katerina's Cafe and Guy's Gyros during dinner time, on the other hand Hippokampos is more popular during lunch time, except for weekends. 


```{r cc daytime, echo= FALSE}

cc_freq_2 <- group_by(cc_data, location, day, hours) %>% summarise(freq = n())%>% arrange(desc(freq))
cc_freq_selected_1 <- cc_freq_2 %>% filter(location == "Katerina's Cafe") %>% arrange(day)
cc_freq_selected_2 <- cc_freq_2 %>% filter(location == "Guy's Gyros") %>% arrange(day)
cc_freq_selected_3 <- cc_freq_2 %>% filter(location == "Hippokampos") %>% arrange(day)

int_plot_cc <- function(cc_freq_selected)
{cc_freq_selected%>%
  plot_ly(
    type = 'bar',
    x = ~hours,
    y = ~freq,
    text = ~day,
    hoverinfo = 'text',
    mode = 'markers',
    transforms = list(
      list(
        type = 'filter',
        target = ~day,
        operation = '=',
        value = unique(cc_freq_selected$day)[2]
      )
  )) %>% layout(
    updatemenus = list(
      list(
        type = 'dropdown',
        buttons = list(
          list(method = "restyle",
               args = list("transforms[0].value", unique(cc_freq_selected$day)[2]),
               label = unique(cc_freq_selected$day)[2]),
          list(method = "restyle",
               args = list("transforms[0].value", unique(cc_freq_selected$day)[6]),
               label = unique(cc_freq_selected$day)[6]),
          list(method = "restyle",
               args = list("transforms[0].value", unique(cc_freq_selected$day)[7]),
               label = unique(cc_freq_selected$day)[7]),
          list(method = "restyle",
               args = list("transforms[0].value", unique(cc_freq_selected$day)[5]),
               label = unique(cc_freq_selected$day)[5]),
          list(method = "restyle",
               args = list("transforms[0].value", unique(cc_freq_selected$day)[1]),
               label = unique(cc_freq_selected$day)[1]),
          list(method = "restyle",
               args = list("transforms[0].value", unique(cc_freq_selected$day)[3]),
               label = unique(cc_freq_selected$day)[3]),
          list(method = "restyle",
               args = list("transforms[0].value", unique(cc_freq_selected$day)[4]),
               label = unique(cc_freq_selected$day)[4])
        )
      )
    )
  ) 
              
}

a <- list(
  text = "Katerina's Cafe",
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

b <- list(
  text = "Guy's Gyros",
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

c <- list(
  text = "Hippokampos",
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)


subplot(int_plot_cc(cc_freq_selected_1) %>% layout(annotations = a),
        int_plot_cc(cc_freq_selected_2) %>% layout(annotations = b),
        int_plot_cc(cc_freq_selected_3) %>% layout(annotations = c), shareY = TRUE, titleX = TRUE) %>% layout(showlegend = FALSE)



```


### Anomalies

1. Mismatch between credit card and loyalty card transactions

As we can see above, the number of daily frequency of transactions are different between credit card data and loyalty card data. Further observations was performed and it shows that there are total of 409 un-matched records. These un-matched records might lead to some new clues. Unmatched records can be seen in the table below


```{r mismatch cc and loyalty data, echo= FALSE}

cc_loyalty = merge(cc_data, loyalty_data, by.x = c("timestamp_date","location","price"), by.y = c("timestamp", "location","price"), all.x = TRUE)

cc_loyalty$timestamp_date <- as.character(cc_loyalty$timestamp_date)
cc_loyalty$timestamp <-  as.character(cc_loyalty$timestamp)

mismatch_cc_loyalty = cc_loyalty %>% filter(is.na(cc_loyalty$loyaltynum)) %>% unique() %>% select(timestamp_date,location,price, timestamp,last4ccnum, loyaltynum)

datatable(mismatch_cc_loyalty)



```
2. Wrong time in credit card transaction data for three coffee shops, Bean There Done That, Brewed Awakenings, and Jack's Magical Beans

To correct this anomaly, we can add vehicle data to our analysis, we might be able to determine some of the transactions based on the employee location. 

```{r wrong time cc_data, echo = FALSE}

cc_selected <- cc_data %>% filter(location %in% c('Bean There Done That','Brewed Awakenings',"Jack's Magical Beans")) %>% select(timestamp,location,price,last4ccnum)

cc_selected$timestamp <- as.character(cc_selected$timestamp)

datatable(cc_selected)

```

```{r gps time duration, include= FALSE}
gps_data <- read_csv("MC2/gps.csv")

gps_data$Timestamp_date <- date_time_parse(gps_data$Timestamp,
                                zone = "",
                                format = "%m/%d/%Y")

gps_data$Timestamp <- date_time_parse(gps_data$Timestamp,
                                zone = "",
                                format = "%m/%d/%Y %H:%M")
gps_data$Time <- format(gps_data$Timestamp, format = "%H:%M")
gps_data$Hour <- get_hour(gps_data$Timestamp)


gps_sort <- gps_data[order(gps_data$Timestamp, gps_data$id),]

stop_fin_2 = data.frame()

for (id_1 in unique(gps_sort$id))
{
  make_stop = data.frame()
  gps_id <- gps_sort %>%
  filter(id==id_1)

  for(i in 1:nrow(gps_id))
  {
    if(i < nrow(gps_id))
    {
      start <- gps_id$Timestamp[i]
      end <- gps_id$Timestamp[i+1]
    } else
    {
      start <- gps_id$Timestamp[i]
      end <- gps_id$Timestamp[i]
      print(start)
    }
    elapsed.time <- start%--%end
    time_duration <- as.duration(elapsed.time)

    if(time_duration > 300)
    {
      make_stop = rbind(make_stop,cbind(gps_id[i,],time_duration,i),cbind(gps_id[i+1,],time_duration,i))
    }

  }

  stop_fin_2 = rbind(stop_fin_2, make_stop)
}
```


```{r location point, include = FALSE}

location_point = read_csv("MC2/stop_fin.csv") %>% select(lat,long,Possible_Location)%>% unique()
stop_fin_2$lat = round(stop_fin_2$lat,5)
stop_fin_2$long = round(stop_fin_2$long,5)

stop_final = merge(stop_fin_2,location_point, by.x = c("lat","long"), by.y = c("lat","long"), all.x = TRUE)

stop_fin <- stop_final


stop_fin_location <- stop_fin[!(stop_fin$Possible_Location %like% 'mice'),]

gps_sf_stopfin <- st_as_sf(stop_fin_location,
                   coords = c("long","lat"),
                   crs=4326)

```


## Question 2
Add the vehicle data to your analysis of the credit and loyalty card data. How does your assessment of the anomalies in question 1 change based on this new data? What discrepancies between vehicle, credit, and loyalty card data do you find? Please limit your answer to 8 images and 500 words.


### Answer
Based on employee location, we can figure out the timing range for cc transaction in Bean There Done That, Brewed Awakenings, Jack's Magical Beans. Even though there are some transaction in Jack's Magical Beans that is not found in location data. 

```{r finding cc timing, echo = FALSE}


cc_selected <- cc_data %>% filter(location %in% c('Bean There Done That','Brewed Awakenings',"Jack's Magical Beans"))

cc2_fixed <- merge(cc_selected,stop_fin, by.x = c("id","timestamp_date","location"), by.y = c("id","Timestamp_date","Possible_Location"), all.x = TRUE) %>%
  select(timestamp, location, price, last4ccnum,id, Timestamp, timestamp_date) %>% group_by(timestamp, location, price, last4ccnum,id, timestamp_date) %>%
  summarize(New_Timestamp = mean(Timestamp) ) %>% ungroup() %>% select(New_Timestamp,location, price, last4ccnum,id, timestamp_date)

colnames(cc2_fixed) <- c('timestamp','location','price','last4ccnum','id','timestamp_date')

cc_data_2<- read_csv("MC2/cc_data.csv") %>% filter(!(location %in% c('Bean There Done That','Brewed Awakenings',"Jack's Magical Beans")))


cc_data_2$timestamp_date <- date_time_parse(cc_data_2$timestamp,
                                 zone = "",
                                format = "%m/%d/%Y")

cc_data_2$timestamp <- date_time_parse(cc_data_2$timestamp,
                                zone = "",
                                format = "%m/%d/%Y %H:%M")

cc_data_fixed <- rbind(cc_data_2,cc2_fixed)


cc_data_fixed$time = format(cc_data$timestamp, format = "%H:%M")
cc_data_fixed$hours = get_hour(cc_data$timestamp)
cc_data_fixed$day = weekdays(cc_data$timestamp)

for(i in 1:nrow(cc_data_fixed))
{
  if(cc_data_fixed$location[i] %like% "Katerina")
  {
   cc_data_fixed$location[i] <- str_replace(cc_data$location[i],cc_data$location[i],"Katerina's Cafe")
  }
}

cc_data_fixed$timestamp <-  as.character(cc_data_fixed$timestamp)
cc_data_fixed$timestamp_date <- as.character(cc_data_fixed$timestamp_date)

cc_data_fixed <- cc_data_fixed %>% select(timestamp,location,price,last4ccnum)

datatable(cc_data_fixed)

```

### Data Discrepancies

1. There are few credit card and loyalty transactions that cannot be traced from the vehicle data. There is a possibility that employee are not using company vehicle to go to a shop or restaurant.

2. There are some shop that is not shown in the maps below for example Abila Zacharo, Hippokampos, Kalami Kafenion. Therefore, it was challenging to figure out the position of some location. Matching the vehicle data with credit card data will help us to figure out some unknown locations, however there are still some shops that are not detected, one of the example is Daily Dealz.

```{r blank map, echo = FALSE}
gps_sf_stopfin_unique1 <- gps_sf_stopfin  %>% select(Possible_Location,geometry)%>%unique()%>%arrange(Possible_Location)

gps_sf_stopfin_unique <- gps_sf_stopfin_unique1[-c(221,476,644,1100,1103),]

gps_path_stopfin <- gps_sf_stopfin_unique %>%
  group_by(Possible_Location) %>%
  summarize(m_Timestamp = mean(geometry),
            do_union = FALSE ) %>%
  st_cast("LINESTRING")


Abila_st <- st_read(dsn = "MC2/Geospatial",
                    layer = "Abila")

P <- npts(Abila_st, by_feature = TRUE)
abila_st_2 <- cbind(Abila_st,P) %>% filter(P > 1)
bgmap <- raster("MC2/Geospatial/MC2-tourist.TIF")

tmap_mode("view")
tm_shape(bgmap) +
  tm_rgb(bgmap, r = 1, g = 2, b = 3,
         alpha = NA,
         saturation = 1,
         interpolate = TRUE,
         max.value = 255) +
  tm_shape(abila_st_2) +
  tm_lines(col = "red", scale = 1)+
  tm_lines(col = "blue", scale =5, interactive = TRUE) 
  
```

Some location that can be traced by using credit card data are Abila Zacharo, Hippokampos, Kalami Kafenion and few other shops.



```{r traced place, echo = FALSE}
gps_sf_stopfin_unique1 <- gps_sf_stopfin  %>% select(Possible_Location,geometry)%>%unique()%>%arrange(Possible_Location)

gps_sf_stopfin_unique <- gps_sf_stopfin_unique1[-c(221,476,644,1100,1103),]

gps_path_stopfin <- gps_sf_stopfin_unique %>%
  group_by(Possible_Location) %>%
  summarize(m_Timestamp = mean(geometry),
            do_union = FALSE ) %>%
  st_cast("LINESTRING")


Abila_st <- st_read(dsn = "MC2/Geospatial",
                    layer = "Abila")

P <- npts(Abila_st, by_feature = TRUE)
abila_st_2 <- cbind(Abila_st,P) %>% filter(P > 1)
bgmap <- raster("MC2/Geospatial/MC2-tourist.TIF")

tmap_mode("view")
tm_shape(bgmap) +
  tm_rgb(bgmap, r = 1, g = 2, b = 3,
         alpha = NA,
         saturation = 1,
         interpolate = TRUE,
         max.value = 255) +
  tm_shape(abila_st_2) +
  tm_lines(col = "red", scale = 1)+
  tm_shape(gps_path_stopfin[c(3,20,47),]) +
  tm_lines(col = "blue", scale =5, interactive = TRUE) +
 tm_text("Possible_Location", size = 2, remove.overlap = TRUE, overwrite.lines = TRUE, just = "top")
  
```

3. As mentioned previously there are some mismatch transaction between credit card and loyalty card


